---
title: "Class 11: Scraping Multiple Webpages"
author: "Jacob Farmer"
date: "2026-09-30"
output: 
  html_document:
    toc: true
    toc_float: true
    numbered_sections: true
    code_download: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning Objectives
-Enable you to scrape multiple webpages (from the same site) using a `for` loop type approach.
- Enable you to scrape multiple webpages (from the same site) using the [purrr package](https://purrr.tidyverse.org/), which is a functional propramming approach.
*Note:* In this process, we will create our own function.

## Re-examining the bulletin example from class 10

Let us try to expand on the example from last class to include the following:
[ACC](https://bulletin.miamioh.edu/courses-instruction/acc/)
[BUS](https://bulletin.miamioh.edu/courses-instruction/bus/)
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa/)
[MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/)

**COMMENT:** obviously, you can repeat your code a few times and change the URL. This will work for a few links but would be tedious for large amounts of scraping. We will follow the **D.R.Y. Principle**, which stands for **Don't Repeat Yourself**.#sc_sccoursedescs >

```{r bulletin}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')

courses_df = data.frame() # initilizing a container to store stuff in the loop.
for (abbrv in dept_abbrv) {
  cat( rep("-", 50) , "\n")
  print(abbrv)
  bulletin_url = paste0(
    'https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/'
  )
  
  webpage = rvest::read_html(bulletin_url)
  
  webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
  webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  print(df$title[1:2])
  courses_df = rbind(courses_df, df)
}

```


## `purrr` approach for the same problem

This is a functional programming approach, and we will write our own function. In R, we use the funtion called `function` to create a function. As apposed to Python, R functions return a single object.

```{r purrr}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')

# This function take an abbrv as a an input and returns a data_frame as an output
scrape_mu_bulletin = function(abbrv){
  bulletin_url = paste0(
    'https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/'
    )
  
  webpage = rvest::read_html(bulletin_url)
  
  webpage |> rvest::html_elements("p.courseblocktitle") |> rvest::html_text2() -> titles
  webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  return(df)
}

test = scrape_mu_bulletin(abbrv = 'eco')

# to use functions from purrr, we will use a map_*(), or a map2_*(), or a pmap_*().
# map uses a functions that takes a single input (or you are only changing a single input).
# map2 uses a function that takes two inputs
# pmap >= 3
# after the _, you put the type of object you are getting back.

# the .x is the vector that we will iterate over
# and the .f is the function we use

courses_df_from_purr = purrr::map_df(.x = dept_abbrv, .f = scrape_mu_bulletin)
```


## Scrape data from the website planecrashinfo

The website that we want to scrape is called: <https://www.planecrashinfo.com/> and it containes a database of plane crashes by year.

```{r}
year = 2025

crash_url = paste0('https://www.planecrashinfo.com/', year, '/', year, '.htm')

crash_page = rvest::read_html()
```




