---
title: "Exam Prep Part 2"
author: "Jacob Farmer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Question 3
```{r}
lst = list( 
  gdp = data.frame(year = c(2020, 2021, 2022), values = c(19200, 20500, 21300), units = "USD billions" ),
  population = list(country = "United States", year = c(2020, 2021, 2022), values = c(325, 331, 335), units = "millions"),
  indicators = c("gdp", "population", "inflation"), # Available indicators
  inflation_rate = 3.2 # Latest inflation rate as a single value
)

lst[[2]]
```

#Question 4
```{r}
hibp_data = jsonlite::fromJSON("../data/hibp_data.json")
```

#Question 5
```{r}
hibp_data[500, ][2]
```

#Question 6
```{r}
hibp_data$Email |> stringr::str_detect("miamioh.edu") |> table()
```

#Question 7
```{r}
robotstxt::paths_allowed("https://en.wikipedia.org/wiki/Miami_University", 
                         bot = "*")
```

#Question 8
```{r}
policy_url = paste0("https://miamioh.edu/policy-library/students/undergraduate/academic-regulations/index.html")

webpage = rvest::read_html(policy_url)

webpage |> rvest::html_elements("a.news-lockup__body-link") |> rvest::html_text2() -> policy_name_vec
webpage |> rvest::html_elements("a.news-lockup__body-link") |>  rvest::html_attr("href") -> mu_policies

```

#Question 9
```{r}
swim_url = paste0("https://miamiredhawks.com/sports/swimming-and-diving/roster")

webpage = rvest::read_html(swim_url)

webpage |> rvest::html_elements("div > a > h3") |> rvest::html_text2() -> swim_names

swim_names = swim_names[1:52]

webpage |> rvest::html_elements(".s-person-details__bio-stats-item:nth-child(2)") |> rvest::html_text2() -> swim_year

swim_year = stringr::str_remove(swim_year, "Academic Year")
swim_df = data.frame(name = swim_names, year = swim_year)

```

#Question 11
```{r}
ip_data = readr::read_csv("../data/toxic_ips_oct2025.csv")

ips = ip_data$IP

ip_function = function(ip_address){
  base_url = "http://ip-api.com/json/"
  end_url = "?fields=status,continent,country,countryCode,region,regionName,city,district,zip,lat,lon,timezone,currency,isp,org,as,query"
  
  full_url = paste0(base_url, ip_address, end_url)
  
  response = jsonlite::fromJSON(full_url) |> dplyr::bind_cols()
  return(response)
}

ip_df = data.frame()
for (ip in ips) {
  df = ip_function(ip_address = ip)
  
  ip_df = rbind(ip_df, df)
}
```

#Question 12
TIDY occurs where:
1) Every column is a variable
2) Every row is an observation
3) Every value is a cell

TECHNICALLY CORRECT data is when:
1) the data type is correct
2) there are relevant column names

#Question 13
```{r}
ntse_data = readr::read_csv("../data/ntse_endowment_us_and_canada_2020.csv")
```

#Question 14
TECHNICALLY CORRECT data is when:
1) the correct data type is used
2) there are relevant column names









